Damage localization based on vibrations

### 2017-03-23 rapport/paper.tex
paper

@@

@@

@@

\section{Results}

@@

\subsection{FRF results}

@@

@@

\subsection{Without noise}

@@

\subsection{With noise}

@@

\subsection{Eliminate the false positives}

@@

\subsection{Beam}

@@

>>>>

Figure (\ref{theo}) shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/theo60.png}
  \caption{Theoretical FRF for undamaged and damage states}
  \label{theo}
\end{figure}

@@

\subsection{False and missing alarm}

@@

Figure(\ref{theodiff}) shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/theodiff60.png}
  \caption{Difference betweem theoretical FRF of undamaged and damage states}
  \label{theodiff}
\end{figure}

@@

We can also use our simulation with other structures, like a beam, if we know the matrices $M$, $K$, $C$ and the impact of a damage on these matrices.
We will also validate the FRF interpolation method with a beam in this paper, but we don't detail the matrices $M$, $K$, $C$.

\section{Analysis}

@@

\subsection{Data presentation}

@@

\subsection{FRF interpolation method results}

@@

\subsubsection{Without noise}

@@

\subsubsection{With noise}

@@

\subsection{Eliminate the false positives to improve the efficiency}

We have seen that there are too many false positives. We try to remove them with the next idea: the difference between the threshold and the computed values is larger on the damage than on other sensors. As the damage is localized on one spring, so between two sensors, we apply the next algorithm to determine where is the damage:
\begin{itemize}
\item We compute the error values
\item We make the difference with the threshold
\item We keep only the two highest values, and we detect a damage only if they are positives
\end{itemize}

Figure (\ref{detect_max}) shows the results of this method.

@@

\subsection{FRF interpolation method on a beam}

@@

We think we can use the FRF method interpolation for a quantification of the damage. For that, we have compared the threshold and the difference between it and the computed error.

We shows in Figure(\ref{quant}) the computed error, in percent of the threshold.
